A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-11 paper.tex
citation for NP-hardness of our fundamental problem

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice \textbf{Cite Koller!!!}, and such a
precision doesn't have any fundamental advantage. Instead, it is
customary compute so-called Nash $\epsilon$-equlibria.

>>>>

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a
precision doesn't have any fundamental practical advantage. Instead, it is
customary compute so-called Nash $\epsilon$-equlibria.
